### 2019-08-05 reports/thesis/book.tex
Update delcaration

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsbsy}
\usepackage{graphicx}
\usepackage[outdir=./]{epstopdf}
\usepackage[round]{natbib} 
\usepackage{url}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{hyphenat}
\usepackage{pdfpages}
\usepackage{MnSymbol} %udots
\usepackage{afterpage} %\afterpage{\clearpage}
\usepackage{siunitx} %for measurements
\usepackage{rotating}
\usepackage{multirow} %for multirow tables
\usepackage{mathtools} %multlined
\usepackage{longtable}

@@

\chapter{Declaration}
This thesis is the author's own work and has not been published at the time of submitting.

This thesis is a result of collaborative research with Inside-out: Statistical methods for Computed Tomography validation of complex structures in Additive Layer Manufacturing funded by EPSRC (EP/K031066/1).  Greg Gibbons and Jay Warnett, from the Warwick Manufacturing Group, were responsible for the fabrication, x-ray computed tomography acquisition and simulation of test samples used in this thesis. In this thesis, they are referred to as engineers.

This thesis has not been submitted for a degree at another university.

>>>>

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsbsy}
\usepackage{graphicx}
\usepackage[outdir=./]{epstopdf}
\usepackage[round]{natbib} 
\usepackage{url}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{hyphenat}
\usepackage{pdfpages}
\usepackage{MnSymbol} %udots
\usepackage{afterpage} %\afterpage{\clearpage}
\usepackage{siunitx} %for measurements
\usepackage[figuresright]{rotating}
\usepackage{multirow} %for multirow tables
\usepackage{mathtools} %multlined
\usepackage{longtable}
\usepackage{bibentry}

@@

\chapter{Declaration}
This thesis is submitted to the University of Warwick in support of my application for the degree of Doctor of Philosophy. It has been composed by myself and has not been submitted in any previous application for any degree.

The work presented (including data generated and data analysis) was carried out by the author except in the cases outlined below:
\begin{itemize}
  \item The fabrication, x-ray computed tomography acquisition and simulation of test samples were done by Greg Gibbons and Jay Warnett, from the Warwick Manufacturing Group, as part of Inside-out: Statistical methods for Computed Tomography validation of complex structures in Additive Layer Manufacturing funded by EPSRC (EP/K031066/1).
\end{itemize}

Parts of this thesis have been published by the author:
\begin{itemize}
  \item\nobibliography*\bibentry{lo2019detection}
\end{itemize}
